---
title: "P1A6 - Forest Plot Visualization"
output: html_notebook
---

# Goal: Forest Graph with EC50s for each Strain x Drug #

# Set Working Directory #
```{r}
rm(list=ls())
setwd("~/Box Sync/DeRisi Lab/Experiments 2020/P1A6 - EC50 Refinement/P1A6-DataVisualization/")
```

# Make a Test Plot with Fluconazole #
#Read in the EC50 and LD50 Data#
```{r}
FlucEC50 <- read.table("Table_Fluconazole.txt", sep="\t", header=TRUE)
FlucLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Fluconazole_Tox.txt", sep="\t",header=TRUE)

FlucCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

FlucCombo[c(1:3),]<- as.matrix(FlucLD50)
FlucCombo[c(4:19),]<-as.matrix(FlucEC50)

write.table(FlucCombo, "Table_LD50_EC50_Fluconazole.txt", sep="\t", quote=F, row.names = F)

FlucCombo <- read.table("Table_LD50_EC50_Fluconazole.txt", header=TRUE, sep="\t")

FlucCombo$Strain <- factor(FlucCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
library(ggplot2)
FlucCombo$Strain <- factor(FlucCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
Graph_Fluc <- ggplot(FlucCombo)+
    geom_point(aes(x=FlucCombo$Strain, y=FlucCombo$EC50))+
    geom_errorbar(aes(x=FlucCombo$Strain, ymin=FlucCombo$EC50.min, ymax=FlucCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Fluc
ggsave(filename="Graph_Forest_Fluc.pdf", plot=Graph_Fluc, useDingbats=FALSE,width=3, height=8, units="in")    
```

#Repeat for All Other Drugs#
# Make a Test Plot with Caspofungin #
#Read in the EC50 and LD50 Data#
```{r}
CaspofunginEC50 <- read.table("Table_Caspofungin.txt", sep="\t", header=TRUE)
CaspofunginLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Caspofungin_Tox.txt", sep="\t",header=TRUE)

CaspofunginCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

CaspofunginCombo[c(1:3),]<- as.matrix(CaspofunginLD50)
CaspofunginCombo[c(4:19),]<-as.matrix(CaspofunginEC50)

write.table(CaspofunginCombo, "Table_LD50_EC50_Caspofungin.txt", sep="\t", quote=F, row.names = F)

CaspofunginCombo <- read.table("Table_LD50_EC50_Caspofungin.txt", header=TRUE, sep="\t")

CaspofunginCombo$Strain <- factor(CaspofunginCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Caspofungin <- ggplot(CaspofunginCombo)+
    geom_point(aes(x=CaspofunginCombo$Strain, y=CaspofunginCombo$EC50))+
    geom_errorbar(aes(x=CaspofunginCombo$Strain, ymin=CaspofunginCombo$EC50.min, ymax=CaspofunginCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Caspofungin
ggsave(filename="Graph_Forest_Caspofungin.pdf", plot=Graph_Caspofungin, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Broxyquinolone #
#Read in the EC50 and LD50 Data#
```{r}
BroxyquinoloneEC50 <- read.table("Table_Broxyquinolone.txt", sep="\t", header=TRUE)
BroxyquinoloneLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Broxyquinolone_Tox.txt", sep="\t",header=TRUE)

BroxyquinoloneCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

BroxyquinoloneCombo[c(1:3),]<- as.matrix(BroxyquinoloneLD50)
BroxyquinoloneCombo[c(4:19),]<-as.matrix(BroxyquinoloneEC50)

write.table(BroxyquinoloneCombo, "Table_LD50_EC50_Broxyquinolone.txt", sep="\t", quote=F, row.names = F)

BroxyquinoloneCombo <- read.table("Table_LD50_EC50_Broxyquinolone.txt", header=TRUE, sep="\t")

BroxyquinoloneCombo$Strain <- factor(BroxyquinoloneCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Broxyquinolone <- ggplot(BroxyquinoloneCombo)+
    geom_point(aes(x=BroxyquinoloneCombo$Strain, y=BroxyquinoloneCombo$EC50))+
    geom_errorbar(aes(x=BroxyquinoloneCombo$Strain, ymin=BroxyquinoloneCombo$EC50.min, ymax=BroxyquinoloneCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Broxyquinolone
ggsave(filename="Graph_Forest_Broxyquinolone.pdf", plot=Graph_Broxyquinolone, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Chloroxine #
#Read in the EC50 and LD50 Data#
```{r}
ChloroxineEC50 <- read.table("Table_Chloroxine.txt", sep="\t", header=TRUE)
ChloroxineLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Chloroxine_Tox.txt", sep="\t",header=TRUE)

ChloroxineCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

ChloroxineCombo[c(1:3),]<- as.matrix(ChloroxineLD50)
ChloroxineCombo[c(4:19),]<-as.matrix(ChloroxineEC50)

write.table(ChloroxineCombo, "Table_LD50_EC50_Chloroxine.txt", sep="\t", quote=F, row.names = F)

ChloroxineCombo <- read.table("Table_LD50_EC50_Chloroxine.txt", header=TRUE, sep="\t")

ChloroxineCombo$Strain <- factor(ChloroxineCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Chloroxine <- ggplot(ChloroxineCombo)+
    geom_point(aes(x=ChloroxineCombo$Strain, y=ChloroxineCombo$EC50))+
    geom_errorbar(aes(x=ChloroxineCombo$Strain, ymin=ChloroxineCombo$EC50.min, ymax=ChloroxineCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Chloroxine
ggsave(filename="Graph_Forest_Chloroxine.pdf", plot=Graph_Chloroxine, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Clioquinol #
#Read in the EC50 and LD50 Data#
```{r}
ClioquinolEC50 <- read.table("Table_Clioquinol.txt", sep="\t", header=TRUE)
ClioquinolLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Clioquinol_Tox.txt", sep="\t",header=TRUE)

ClioquinolCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

ClioquinolCombo[c(1:3),]<- as.matrix(ClioquinolLD50)
ClioquinolCombo[c(4:19),]<-as.matrix(ClioquinolEC50)

write.table(ClioquinolCombo, "Table_LD50_EC50_Clioquinol.txt", sep="\t", quote=F, row.names = F)

ClioquinolCombo <- read.table("Table_LD50_EC50_Clioquinol.txt", header=TRUE, sep="\t")

ClioquinolCombo$Strain <- factor(ClioquinolCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Clioquinol <- ggplot(ClioquinolCombo)+
    geom_point(aes(x=ClioquinolCombo$Strain, y=ClioquinolCombo$EC50))+
    geom_errorbar(aes(x=ClioquinolCombo$Strain, ymin=ClioquinolCombo$EC50.min, ymax=ClioquinolCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Clioquinol
ggsave(filename="Graph_Forest_Clioquinol.pdf", plot=Graph_Clioquinol, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Cloxiquine #
#Read in the EC50 and LD50 Data#
```{r}
CloxiquineEC50 <- read.table("Table_Cloxiquine.txt", sep="\t", header=TRUE)
CloxiquineLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Cloxiquine_Tox.txt", sep="\t",header=TRUE)

CloxiquineCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

CloxiquineCombo[c(1:3),]<- as.matrix(CloxiquineLD50)
CloxiquineCombo[c(4:19),]<-as.matrix(CloxiquineEC50)

write.table(CloxiquineCombo, "Table_LD50_EC50_Cloxiquine.txt", sep="\t", quote=F, row.names = F)

CloxiquineCombo <- read.table("Table_LD50_EC50_Cloxiquine.txt", header=TRUE, sep="\t")

CloxiquineCombo$Strain <- factor(CloxiquineCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Cloxiquine <- ggplot(CloxiquineCombo)+
    geom_point(aes(x=CloxiquineCombo$Strain, y=CloxiquineCombo$EC50))+
    geom_errorbar(aes(x=CloxiquineCombo$Strain, ymin=CloxiquineCombo$EC50.min, ymax=CloxiquineCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Cloxiquine
ggsave(filename="Graph_Forest_Cloxiquine.pdf", plot=Graph_Cloxiquine, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Disulfiram #
#Read in the EC50 and LD50 Data#
```{r}
DisulfiramEC50 <- read.table("Table_Disulfiram.txt", sep="\t", header=TRUE)
DisulfiramLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Disulfiram_Tox.txt", sep="\t",header=TRUE)

DisulfiramCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

DisulfiramCombo[c(1:3),]<- as.matrix(DisulfiramLD50)
DisulfiramCombo[c(4:19),]<-as.matrix(DisulfiramEC50)

write.table(DisulfiramCombo, "Table_LD50_EC50_Disulfiram.txt", sep="\t", quote=F, row.names = F)

DisulfiramCombo <- read.table("Table_LD50_EC50_Disulfiram.txt", header=TRUE, sep="\t")

DisulfiramCombo$Strain <- factor(DisulfiramCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Disulfiram <- ggplot(DisulfiramCombo)+
    geom_point(aes(x=DisulfiramCombo$Strain, y=DisulfiramCombo$EC50))+
    geom_errorbar(aes(x=DisulfiramCombo$Strain, ymin=DisulfiramCombo$EC50.min, ymax=DisulfiramCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Disulfiram
ggsave(filename="Graph_Forest_Disulfiram.pdf", plot=Graph_Disulfiram, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Miltefosine #
#Read in the EC50 and LD50 Data#
```{r}
MiltefosineEC50 <- read.table("Table_Miltefosine.txt", sep="\t", header=TRUE)
MiltefosineLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Miltefosine_Tox.txt", sep="\t",header=TRUE)

MiltefosineCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

MiltefosineCombo[c(1:3),]<- as.matrix(MiltefosineLD50)[c(1:3),]
MiltefosineCombo[c(4:19),]<-as.matrix(MiltefosineEC50)

write.table(MiltefosineCombo, "Table_LD50_EC50_Miltefosine.txt", sep="\t", quote=F, row.names = F)

MiltefosineCombo <- read.table("Table_LD50_EC50_Miltefosine.txt", header=TRUE, sep="\t")

MiltefosineCombo$Strain <- factor(MiltefosineCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Miltefosine <- ggplot(MiltefosineCombo)+
    geom_point(aes(x=MiltefosineCombo$Strain, y=MiltefosineCombo$EC50))+
    geom_errorbar(aes(x=MiltefosineCombo$Strain, ymin=MiltefosineCombo$EC50.min, ymax=MiltefosineCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Miltefosine
ggsave(filename="Graph_Forest_Miltefosine.pdf", plot=Graph_Miltefosine, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Nitroxiline #
#Read in the EC50 and LD50 Data#
```{r}
NitroxilineEC50 <- read.table("Table_Nitroxiline.txt", sep="\t", header=TRUE)
NitroxilineLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Nitroxiline_Tox.txt", sep="\t",header=TRUE)

NitroxilineCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

NitroxilineCombo[c(1:3),]<- as.matrix(NitroxilineLD50)
NitroxilineCombo[c(4:19),]<-as.matrix(NitroxilineEC50)

write.table(NitroxilineCombo, "Table_LD50_EC50_Nitroxiline.txt", sep="\t", quote=F, row.names = F)

NitroxilineCombo <- read.table("Table_LD50_EC50_Nitroxiline.txt", header=TRUE, sep="\t")

NitroxilineCombo$Strain <- factor(NitroxilineCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Nitroxiline <- ggplot(NitroxilineCombo)+
    geom_point(aes(x=NitroxilineCombo$Strain, y=NitroxilineCombo$EC50))+
    geom_errorbar(aes(x=NitroxilineCombo$Strain, ymin=NitroxilineCombo$EC50.min, ymax=NitroxilineCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Nitroxiline
ggsave(filename="Graph_Forest_Nitroxiline.pdf", plot=Graph_Nitroxiline, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with OSU_03012 #
#Read in the EC50 and LD50 Data#
```{r}
OSU_03012EC50 <- read.table("Table_OSU_03012.txt", sep="\t", header=TRUE)
OSU_03012LD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_OSU_03012_Tox.txt", sep="\t",header=TRUE)

OSU_03012Combo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

OSU_03012Combo[c(1:3),]<- as.matrix(OSU_03012LD50)
OSU_03012Combo[c(4:19),]<-as.matrix(OSU_03012EC50)

write.table(OSU_03012Combo, "Table_LD50_EC50_OSU_03012.txt", sep="\t", quote=F, row.names = F)

OSU_03012Combo <- read.table("Table_LD50_EC50_OSU_03012.txt", header=TRUE, sep="\t")

OSU_03012Combo$Strain <- factor(OSU_03012Combo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_OSU_03012 <- ggplot(OSU_03012Combo)+
    geom_point(aes(x=OSU_03012Combo$Strain, y=OSU_03012Combo$EC50))+
    geom_errorbar(aes(x=OSU_03012Combo$Strain, ymin=OSU_03012Combo$EC50.min, ymax=OSU_03012Combo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_OSU_03012
ggsave(filename="Graph_Forest_OSU_03012.pdf", plot=Graph_OSU_03012, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Caspofungin #
#Read in the EC50 and LD50 Data#
```{r}
CaspofunginEC50 <- read.table("Table_Caspofungin.txt", sep="\t", header=TRUE)
CaspofunginLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Caspofungin_Tox.txt", sep="\t",header=TRUE)

CaspofunginCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

CaspofunginCombo[c(1:3),]<- as.matrix(CaspofunginLD50)
CaspofunginCombo[c(4:19),]<-as.matrix(CaspofunginEC50)

write.table(CaspofunginCombo, "Table_LD50_EC50_Caspofungin.txt", sep="\t", quote=F, row.names = F)

CaspofunginCombo <- read.table("Table_LD50_EC50_Caspofungin.txt", header=TRUE, sep="\t")

CaspofunginCombo$Strain <- factor(CaspofunginCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Caspofungin <- ggplot(CaspofunginCombo)+
    geom_point(aes(x=CaspofunginCombo$Strain, y=CaspofunginCombo$EC50))+
    geom_errorbar(aes(x=CaspofunginCombo$Strain, ymin=CaspofunginCombo$EC50.min, ymax=CaspofunginCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Caspofungin
ggsave(filename="Graph_Forest_Caspofungin.pdf", plot=Graph_Caspofungin, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Pentamidine #
#Read in the EC50 and LD50 Data#
```{r}
PentamidineEC50 <- read.table("Table_Pentamidine.txt", sep="\t", header=TRUE)
PentamidineLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Pentamidine_Tox.txt", sep="\t",header=TRUE)

PentamidineCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

PentamidineCombo[c(1:3),]<- as.matrix(PentamidineLD50)
PentamidineCombo[c(4:19),]<-as.matrix(PentamidineEC50)

write.table(PentamidineCombo, "Table_LD50_EC50_Pentamidine.txt", sep="\t", quote=F, row.names = F)

PentamidineCombo <- read.table("Table_LD50_EC50_Pentamidine.txt", header=TRUE, sep="\t")

PentamidineCombo$Strain <- factor(PentamidineCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Pentamidine <- ggplot(PentamidineCombo)+
    geom_point(aes(x=PentamidineCombo$Strain, y=PentamidineCombo$EC50))+
    geom_errorbar(aes(x=PentamidineCombo$Strain, ymin=PentamidineCombo$EC50.min, ymax=PentamidineCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Pentamidine
ggsave(filename="Graph_Forest_Pentamidine.pdf", plot=Graph_Pentamidine, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Posaconazole #
#Read in the EC50 and LD50 Data#
```{r}
PosaconazoleEC50 <- read.table("Table_Posaconazole.txt", sep="\t", header=TRUE)
PosaconazoleLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Posaconazole_Tox.txt", sep="\t",header=TRUE)

PosaconazoleCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

PosaconazoleCombo[c(1:3),]<- as.matrix(PosaconazoleLD50)
PosaconazoleCombo[c(4:19),]<-as.matrix(PosaconazoleEC50)

write.table(PosaconazoleCombo, "Table_LD50_EC50_Posaconazole.txt", sep="\t", quote=F, row.names = F)

PosaconazoleCombo <- read.table("Table_LD50_EC50_Posaconazole.txt", header=TRUE, sep="\t")

PosaconazoleCombo$Strain <- factor(PosaconazoleCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Posaconazole <- ggplot(PosaconazoleCombo)+
    geom_point(aes(x=PosaconazoleCombo$Strain, y=PosaconazoleCombo$EC50))+
    geom_errorbar(aes(x=PosaconazoleCombo$Strain, ymin=PosaconazoleCombo$EC50.min, ymax=PosaconazoleCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Posaconazole
ggsave(filename="Graph_Forest_Posaconazole.pdf", plot=Graph_Posaconazole, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Terbinafine #
#Read in the EC50 and LD50 Data#
```{r}
TerbinafineEC50 <- read.table("Table_Terbinafine.txt", sep="\t", header=TRUE)
TerbinafineLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Terbinafine_Tox.txt", sep="\t",header=TRUE)

TerbinafineCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

TerbinafineCombo[c(1:3),]<- as.matrix(TerbinafineLD50)
TerbinafineCombo[c(4:19),]<-as.matrix(TerbinafineEC50)

write.table(TerbinafineCombo, "Table_LD50_EC50_Terbinafine.txt", sep="\t", quote=F, row.names = F)

TerbinafineCombo <- read.table("Table_LD50_EC50_Terbinafine.txt", header=TRUE, sep="\t")

TerbinafineCombo$Strain <- factor(TerbinafineCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Terbinafine <- ggplot(TerbinafineCombo)+
    geom_point(aes(x=TerbinafineCombo$Strain, y=TerbinafineCombo$EC50))+
    geom_errorbar(aes(x=TerbinafineCombo$Strain, ymin=TerbinafineCombo$EC50.min, ymax=TerbinafineCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Terbinafine
ggsave(filename="Graph_Forest_Terbinafine.pdf", plot=Graph_Terbinafine, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Triclabendazole #
#Read in the EC50 and LD50 Data#
```{r}
TriclabendazoleEC50 <- read.table("Table_Triclabendazole.txt", sep="\t", header=TRUE)
TriclabendazoleLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Triclabendazole_Tox.txt", sep="\t",header=TRUE)

TriclabendazoleCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

TriclabendazoleCombo[c(1:3),]<- as.matrix(TriclabendazoleLD50)
TriclabendazoleCombo[c(4:19),]<-as.matrix(TriclabendazoleEC50)

write.table(TriclabendazoleCombo, "Table_LD50_EC50_Triclabendazole.txt", sep="\t", quote=F, row.names = F)

TriclabendazoleCombo <- read.table("Table_LD50_EC50_Triclabendazole.txt", header=TRUE, sep="\t")

TriclabendazoleCombo$Strain <- factor(TriclabendazoleCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Triclabendazole <- ggplot(TriclabendazoleCombo)+
    geom_point(aes(x=TriclabendazoleCombo$Strain, y=TriclabendazoleCombo$EC50))+
    geom_errorbar(aes(x=TriclabendazoleCombo$Strain, ymin=TriclabendazoleCombo$EC50.min, ymax=TriclabendazoleCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Triclabendazole
ggsave(filename="Graph_Forest_Triclabendazole.pdf", plot=Graph_Triclabendazole, useDingbats=FALSE,width=3, height=8, units="in")    
```

# Make a Test Plot with Amphotericine #
#Read in the EC50 and LD50 Data#
```{r}
AmphotericineEC50 <- read.table("Table_Amphotericine.txt", sep="\t", header=TRUE)
AmphotericineLD50 <- read.table("~/Box Sync/DeRisi Lab/Experiments 2020/P1A7 - Drug toxicity data/P1A7-DataProcessing/Table_Amphotericine_Tox.txt", sep="\t",header=TRUE)

AmphotericineCombo <- matrix(data = NA, nrow =  19, ncol = 4, dimnames=list(c(1:19),c("Strain","EC50","EC50.min","EC50.max")))

AmphotericineCombo[c(1:3),]<- as.matrix(AmphotericineLD50)
AmphotericineCombo[c(4:19),]<-as.matrix(AmphotericineEC50)

write.table(AmphotericineCombo, "Table_LD50_EC50_Amphotericine.txt", sep="\t", quote=F, row.names = F)

AmphotericineCombo <- read.table("Table_LD50_EC50_Amphotericine.txt", header=TRUE, sep="\t")

AmphotericineCombo$Strain <- factor(AmphotericineCombo$Strain, c("Strain1642", "Strain1546", "Strain1544", "Strain1542", "Strain1541", "Strain1643", "Strain1641", "Strain1545", "Strain1540", "Strain1539", "StrainB8", "StrainB3", "Strain124", "Strain1543", "Strain1538", "Strain1537", "Hff", "Hep", "HEK293"))
                           
```

#Make a Forest Plot#
```{r}
Graph_Amphotericine <- ggplot(AmphotericineCombo)+
    geom_point(aes(x=AmphotericineCombo$Strain, y=AmphotericineCombo$EC50))+
    geom_errorbar(aes(x=AmphotericineCombo$Strain, ymin=AmphotericineCombo$EC50.min, ymax=AmphotericineCombo$EC50.max))+
    theme_classic() +scale_fill_brewer(palette = "Greys", direction=1)+
    scale_y_log10(limits=c(0.01,10000),breaks=c(0.01,0.1,1,10,100,1000,10000))+
    coord_flip()
Graph_Amphotericine
ggsave(filename="Graph_Forest_Amphotericine.pdf", plot=Graph_Amphotericine, useDingbats=FALSE,width=3, height=8, units="in")    
```