---
title: "P1A6 - Clioquinol Graphs"
output: html_notebook
---

#Set Working Directory
```{r}
rm(list=ls())
setwd("~/Box Sync/DeRisi Lab/Experiments 2020/P1A6 - EC50 Refinement/P1A6-DataProcessing/")
```

#Read in Data
```{r}
P1A6_24hr_BR1 <- read.table("P1A6-24hr_Data_BR1.txt", sep="\t", header=TRUE)
P1A6_24hr_BR2 <- read.table("P1A6-24hr_Data_BR2.txt", sep="\t", header=TRUE)
P1A6_24hr_BR3 <- read.table("P1A6-24hr_Data_BR3.txt", sep="\t", header=TRUE)

P1A6_R_BR1 <- P1A6_24hr_BR1[,c(1,2,3,5,8)]
P1A6_R_BR2<- P1A6_24hr_BR2[,c(1,2,3,5,8)]
P1A6_R_BR3<- P1A6_24hr_BR3[,c(1,2,3,5,8)]
P1A6_R_BR1$BiologicRepeat <- "BR1"
P1A6_R_BR2$BiologicRepeat<- "BR2"
P1A6_R_BR3$BiologicRepeat<- "BR3"

P1A6_R <- rbind(P1A6_R_BR1,P1A6_R_BR2,P1A6_R_BR3)
write.table(P1A6_R,"P1A6-24h_AllRepeats_Long.txt",sep="\t",row.names=F,quote=F)

P1A6_Wide<- P1A6_R_BR1[,c(1:4)]
P1A6_Wide$BR1_BackgroundCorr <- P1A6_R_BR1[,c(5)]
P1A6_Wide$BR2_BackgroundCorr <- P1A6_R_BR2[,c(5)]
P1A6_Wide$BR3_BackgroundCorr <- P1A6_R_BR3[,c(5)]
write.table(P1A6_Wide,"P1A6-24h_AllRepeats_Wide.txt",sep="\t",row.names=F,quote=F)

Clioquinol <- subset(P1A6_R, P1A6_R$Drug=="Clioquinol" & P1A6_R$Concentration>0 & P1A6_R$Concentration<15)
```

#Load Libraries 
```{r}
library(plyr)
library(reshape2)
library(ggplot2)
library(nplr)
library(gridExtra)
```

#Take a look at DMSO Controls#
```{r}
levels(P1A6_R$Drug)
DMSO <- subset(P1A6_Wide, P1A6_Wide$Drug=="DMSO-100" | P1A6_Wide$Drug=="DMSO-1000" | P1A6_Wide$Drug=="DMSO-250" | P1A6_Wide$Drug=="DMSO-500")

DMSO$AverageCorr <- (DMSO$BR1_BackgroundCorr+DMSO$BR2_BackgroundCorr+DMSO$BR3_BackgroundCorr)/3

#Begin by Subsetting Data by Strain#
Strain1537 <- subset(DMSO, DMSO$Strain == "Strain1537")
Strain1538 <- subset(DMSO, DMSO$Strain == "Strain1538")
Strain1539 <- subset(DMSO, DMSO$Strain == "Strain1539")
Strain1540 <- subset(DMSO, DMSO$Strain == "Strain1540")
Strain1541 <- subset(DMSO, DMSO$Strain == "Strain1541")
Strain1542 <- subset(DMSO, DMSO$Strain == "Strain1542")
Strain1543 <- subset(DMSO, DMSO$Strain == "Strain1543")
Strain1544 <- subset(DMSO, DMSO$Strain == "Strain1544")
Strain1545 <- subset(DMSO, DMSO$Strain == "Strain1545")
Strain1546 <- subset(DMSO, DMSO$Strain == "Strain1546")
Strain1641 <- subset(DMSO, DMSO$Strain == "Strain1641")
Strain1642 <- subset(DMSO, DMSO$Strain == "Strain1642")
Strain1643 <- subset(DMSO, DMSO$Strain == "Strain1643")
Strain124 <- subset(DMSO, DMSO$Strain == "Strain124")
StrainB3 <- subset(DMSO, DMSO$Strain == "StrainB3")
StrainB8 <- subset(DMSO, DMSO$Strain == "StrainB8")

#Calculate Mean for Each Strain#
DMSO_mean_Strain1537 <- mean(Strain1537$AverageCorr)
DMSO_mean_Strain1538 <- mean(Strain1538$AverageCorr)
DMSO_mean_Strain1539 <- mean(Strain1539$AverageCorr)
DMSO_mean_Strain1540 <- mean(Strain1540$AverageCorr)
DMSO_mean_Strain1541 <- mean(Strain1541$AverageCorr)
DMSO_mean_Strain1542 <- mean(Strain1542$AverageCorr)
DMSO_mean_Strain1543 <- mean(Strain1543$AverageCorr)
DMSO_mean_Strain1544 <- mean(Strain1544$AverageCorr)
DMSO_mean_Strain1545 <- mean(Strain1545$AverageCorr)
DMSO_mean_Strain1546 <- mean(Strain1546$AverageCorr)
DMSO_mean_Strain1641 <- mean(Strain1641$AverageCorr)
DMSO_mean_Strain1642 <- mean(Strain1642$AverageCorr)
DMSO_mean_Strain1643 <- mean(Strain1643$AverageCorr)
DMSO_mean_Strain124 <- mean(Strain124$AverageCorr)
DMSO_mean_StrainB3 <- mean(StrainB3$AverageCorr)
DMSO_mean_StrainB8 <- mean(StrainB8$AverageCorr)
```

#Subset Clioquinol by Strain#
```{r}
#Begin by Subsetting Data by Strain#
Strain1537 <- subset(Clioquinol, Clioquinol$Strain == "Strain1537")
Strain1538 <- subset(Clioquinol, Clioquinol$Strain == "Strain1538")
Strain1539 <- subset(Clioquinol, Clioquinol$Strain == "Strain1539")
Strain1540 <- subset(Clioquinol, Clioquinol$Strain == "Strain1540")
Strain1541 <- subset(Clioquinol, Clioquinol$Strain == "Strain1541")
Strain1542 <- subset(Clioquinol, Clioquinol$Strain == "Strain1542")
Strain1543 <- subset(Clioquinol, Clioquinol$Strain == "Strain1543")
Strain1544 <- subset(Clioquinol, Clioquinol$Strain == "Strain1544")
Strain1545 <- subset(Clioquinol, Clioquinol$Strain == "Strain1545")
Strain1546 <- subset(Clioquinol, Clioquinol$Strain == "Strain1546")
Strain1641 <- subset(Clioquinol, Clioquinol$Strain == "Strain1641")
Strain1642 <- subset(Clioquinol, Clioquinol$Strain == "Strain1642")
Strain1643 <- subset(Clioquinol, Clioquinol$Strain == "Strain1643")
Strain124 <- subset(Clioquinol, Clioquinol$Strain == "Strain124")
StrainB3 <- subset(Clioquinol, Clioquinol$Strain == "StrainB3")
StrainB8 <- subset(Clioquinol, Clioquinol$Strain == "StrainB8")
```

#Calculate Percent Inhibition for Clioquinol for Each Strain using DMSO_mean_Strain#
```{r}
Strain1537$PercentInhib <- 1-(Strain1537$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1537 - min(Clioquinol$BackgroundCorrect))
Strain1537_R <- Strain1537[,c(3,1,2,7)]
Strain1537_Summary <- ddply(Strain1537_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1538$PercentInhib <- 1-(Strain1538$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1538 - min(Clioquinol$BackgroundCorrect))
Strain1538_R <- Strain1538[,c(3,1,2,7)]
Strain1538_Summary <- ddply(Strain1538_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1539$PercentInhib <- 1-(Strain1539$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1539 - min(Clioquinol$BackgroundCorrect))
Strain1539_R <- Strain1539[,c(3,1,2,7)]
Strain1539_Summary <- ddply(Strain1539_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1540$PercentInhib <- 1-(Strain1540$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1540 - min(Clioquinol$BackgroundCorrect))
Strain1540_R <- Strain1540[,c(3,1,2,7)]
Strain1540_Summary <- ddply(Strain1540_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1541$PercentInhib <- 1-(Strain1541$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1541 - min(Clioquinol$BackgroundCorrect))
Strain1541_R <- Strain1541[,c(3,1,2,7)]
Strain1541_Summary <- ddply(Strain1541_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1542$PercentInhib <- 1-(Strain1542$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1542 - min(Clioquinol$BackgroundCorrect))
Strain1542_R <- Strain1542[,c(3,1,2,7)]
Strain1542_Summary <- ddply(Strain1542_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1543$PercentInhib <- 1-(Strain1543$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1543 - min(Clioquinol$BackgroundCorrect))
Strain1543_R <- Strain1543[,c(3,1,2,7)]
Strain1543_Summary <- ddply(Strain1543_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1544$PercentInhib <- 1-(Strain1544$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1544 - min(Clioquinol$BackgroundCorrect))
Strain1544_R <- Strain1544[,c(3,1,2,7)]
Strain1544_Summary <- ddply(Strain1544_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1545$PercentInhib <- 1-(Strain1545$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1545 - min(Clioquinol$BackgroundCorrect))
Strain1545_R <- Strain1545[,c(3,1,2,7)]
Strain1545_Summary <- ddply(Strain1545_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1546$PercentInhib <- 1-(Strain1546$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1546 - min(Clioquinol$BackgroundCorrect))
Strain1546_R <- Strain1546[,c(3,1,2,7)]
Strain1546_Summary <- ddply(Strain1546_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1641$PercentInhib <- 1-(Strain1641$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1641 - min(Clioquinol$BackgroundCorrect))
Strain1641_R <- Strain1641[,c(3,1,2,7)]
Strain1641_Summary <- ddply(Strain1641_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1642$PercentInhib <- 1-(Strain1642$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1642 - min(Clioquinol$BackgroundCorrect))
Strain1642_R <- Strain1642[,c(3,1,2,7)]
Strain1642_Summary <- ddply(Strain1642_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain1643$PercentInhib <- 1-(Strain1643$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain1643 - min(Clioquinol$BackgroundCorrect))
Strain1643_R <- Strain1643[,c(3,1,2,7)]
Strain1643_Summary <- ddply(Strain1643_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

Strain124$PercentInhib <- 1-(Strain124$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_Strain124 - min(Clioquinol$BackgroundCorrect))
Strain124_R <- Strain124[,c(3,1,2,7)]
Strain124_Summary <- ddply(Strain124_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

StrainB3$PercentInhib <- 1-(StrainB3$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_StrainB3 - min(Clioquinol$BackgroundCorrect))
StrainB3_R <- StrainB3[,c(3,1,2,7)]
StrainB3_Summary <- ddply(StrainB3_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))

StrainB8$PercentInhib <- 1-(StrainB8$BackgroundCorrect - min(Clioquinol$BackgroundCorrect))/(DMSO_mean_StrainB8 - min(Clioquinol$BackgroundCorrect))
StrainB8_R <- StrainB8[,c(3,1,2,7)]
StrainB8_Summary <- ddply(StrainB8_R, c("Strain","Drug","Concentration"),summarize, mean_PercentInhib=mean(PercentInhib),min_PercentInhib=mean(PercentInhib)-sd(PercentInhib),max_PercentInhib=mean(PercentInhib)+sd(PercentInhib))
```

#Group Strains By Susceptibility to Clioquinol
```{r}
FlucS <- c("Strain1537", "Strain1538","Strain1543","Strain124","StrainB3","StrainB8")
FlucM <- c("Strain1539", "Strain1540","Strain1545","Strain1641","Strain1643")
FlucR <- c("Strain1541","Strain1542","Strain1544","Strain1546","Strain1642")
```

#HEX Codes for the UCSF Color Palatte
```{r}
Navy <- "#052049"
Navy01 <- "#506380"
Blue <- "#178CCB"
Blue01 <- "#5DAFDB"
Orange <- "#F48024"
Orange01<- "#F7A665"
Cyan <- "#18A3AC"
Cyan01 <- "#5DBFC5"
Green <- "#90DB31"
Green01 <- "#B1D16F"
Purple <- "#716FB2"
Purple01 <- "#9C8AC9"
Pink <- "#EC1848"
Pink01 <- "#F25D7F"
Yellow <- "#FFDD00"
Yellow01 <- "#FFE74D"
```

#Model Each Strain for FlucS and Clioquinol
```{r}
get_estimates <- function(Concentration,Inhibition) {
    model <- nplr(Concentration,Inhibition)
    x<- getXcurve(model)
    y<- getYcurve(model)
    EC50 <- getEstimates(model,0.5)[c(1),c(3)]
    EC50_min <- getEstimates(model,0.5)[c(1),c(2)] 
    EC50_max <- getEstimates(model,0.5)[c(1),c(4)]
    estimates<- matrix(data = NA, nrow =  200, ncol = 5, dimnames=list(c(1:200),c("x","y","EC50","EC50-min","EC50-max")))
    estimates[,c(1)]<-x
    estimates[,c(2)]<-y
    estimates[c(1),c(3)]<-EC50
    estimates[c(1),c(4)]<-EC50_min
    estimates[c(1),c(5)]<-EC50_max
    as.data.frame(estimates)
}
    

estimates_1537<- get_estimates(Strain1537$Concentration,Strain1537$PercentInhib)
estimates_1538<- get_estimates(Strain1538$Concentration,Strain1538$PercentInhib)
estimates_1543<- get_estimates(Strain1543$Concentration,Strain1543$PercentInhib)
estimates_124<- get_estimates(Strain124$Concentration,Strain124$PercentInhib)
estimates_B3<- get_estimates(StrainB3$Concentration,StrainB3$PercentInhib)
estimates_B8<- get_estimates(StrainB8$Concentration,StrainB8$PercentInhib)

```

#Graph the FlucS Strains and Clioquinol#
```{r}
GRAPH_Clioquinol_S <- ggplot(Strain1537_Summary)+
    geom_point(aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1537"))+
    geom_line(data=estimates_1537, aes(x=estimates_1537$x, y=estimates_1537$y, color="Strain1537"))+
    geom_point(data=Strain1538_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1538"))+
    geom_line(data=estimates_1538, aes(x=estimates_1538$x, y=estimates_1538$y, color="Strain1538"))+
    geom_point(data=Strain1543_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1543"))+
    geom_line(data=estimates_1543, aes(x=estimates_1543$x, y=estimates_1543$y,color="Strain1543"))+
    geom_point(data=Strain124_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain124"))+
    geom_line(data=estimates_124, aes(x=estimates_124$x, y=estimates_124$y,color="Strain124"))+
    geom_point(data=StrainB3_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="StrainB3"))+
    geom_line(data=estimates_B3, aes(x=estimates_B3$x, y=estimates_B3$y,color="StrainB3"))+
    geom_point(data=StrainB8_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="StrainB8"))+
    geom_line(data=estimates_B8, aes(x=estimates_B8$x, y=estimates_B8$y,color="StrainB8"))+
    scale_x_continuous(breaks=c(-3,-2,-1,0,1,2,3))+
    ylim(-0.35,1.25)+
    xlim(-3,3)+
    xlab("Clioquinol (uM)") + ylab("Percent Inhibition")+
    scale_color_manual(values=c(Green,Navy,Orange,Pink,Cyan,Purple))+
    ggtitle("Susceptible Strains")+
    theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
GRAPH_Clioquinol_S
ggsave(filename="GRAPH-Average_Clioquinol_S.pdf", plot=GRAPH_Clioquinol_S, useDingbats=FALSE, width=11, height=8.5, units="in")


Table <- matrix(data = NA, nrow =  6, ncol = 4, dimnames=list(c(1:6),c("Strain","EC50","EC50-min","EC50-max")))
Table[c(1:6),c(1)] <- FlucS
Table[c(1),c(2:4)] <- as.matrix(estimates_1537[c(1),c(3:5)])
Table[c(2),c(2:4)] <- as.matrix(estimates_1538[c(1),c(3:5)])
Table[c(3),c(2:4)] <- as.matrix(estimates_1543[c(1),c(3:5)])
Table[c(4),c(2:4)] <- as.matrix(estimates_124[c(1),c(3:5)])
Table[c(5),c(2:4)] <- as.matrix(estimates_B3[c(1),c(3:5)])
Table[c(6),c(2:4)] <- as.matrix(estimates_B8[c(1),c(3:5)])

Table_Clioquinol_S <- Table
write.table(Table_Clioquinol_S,"Table_Clioquinol_S.txt", sep="\t", quote=F, row.names = F)

```

#Model Each Strain for FlucM and Clioquinol
```{r}
FlucM

estimates_1539 <- get_estimates(Strain1539$Concentration,Strain1539$PercentInhib)
estimates_1540 <- get_estimates(Strain1540$Concentration,Strain1540$PercentInhib)
estimates_1545 <- get_estimates(Strain1545$Concentration,Strain1545$PercentInhib)
estimates_1641 <- get_estimates(Strain1641$Concentration,Strain1641$PercentInhib)
estimates_1643 <- get_estimates(Strain1643$Concentration,Strain1643$PercentInhib)

```

#Graph the FlucM Strains and Clioquinol#
```{r}
GRAPH_Clioquinol_M <- ggplot(Strain1539_Summary)+
    geom_point(aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1539"))+
    geom_line(data=estimates_1539, aes(x=estimates_1539$x, y=estimates_1539$y, color="Strain1539"))+
    geom_point(data=Strain1540_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1540"))+
    geom_line(data=estimates_1540, aes(x=estimates_1540$x, y=estimates_1540$y, color="Strain1540"))+
    geom_point(data=Strain1545_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1545"))+
    geom_line(data=estimates_1545, aes(x=estimates_1545$x, y=estimates_1545$y,color="Strain1545"))+
    geom_point(data=Strain1641_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1641"))+
    geom_line(data=estimates_1641, aes(x=estimates_1641$x, y=estimates_1641$y,color="Strain1641"))+
    geom_point(data=Strain1643_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1643"))+
    geom_line(data=estimates_1643, aes(x=estimates_1643$x, y=estimates_1643$y,color="Strain1643"))+
    scale_x_continuous(breaks=c(-3,-2,-1,0,1,2,3))+
    ylim(-0.35,1.25)+
    xlim(-3,3)+
    xlab("Clioquinol (uM)") + ylab("Percent Inhibition")+
    scale_color_manual(values=c(Green,Navy,Orange,Pink,Cyan,Purple))+
    ggtitle("Susceptible Strains")+
    theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
GRAPH_Clioquinol_M
ggsave(filename="GRAPH-Average_Clioquinol_M.pdf", plot=GRAPH_Clioquinol_M, useDingbats=FALSE, width=11, height=8.5, units="in")

Table <- matrix(data = NA, nrow =  5, ncol = 4, dimnames=list(c(1:5),c("Strain","EC50","EC50-min","EC50-max")))
Table[c(1:5),c(1)] <- FlucM
Table[c(1),c(2:4)] <- as.matrix(estimates_1539[c(1),c(3:5)])
Table[c(2),c(2:4)] <- as.matrix(estimates_1540[c(1),c(3:5)])
Table[c(3),c(2:4)] <- as.matrix(estimates_1545[c(1),c(3:5)])
Table[c(4),c(2:4)] <- as.matrix(estimates_1641[c(1),c(3:5)])
Table[c(5),c(2:4)] <- as.matrix(estimates_1643[c(1),c(3:5)])

Table_Clioquinol_M <- Table
write.table(Table_Clioquinol_M,"Table_Clioquinol_M.txt", sep="\t", quote=F, row.names = F)
```

#Model Each Strain for FlucR and Clioquinol
```{r}
FlucR

estimates_1541 <- get_estimates(Strain1541$Concentration,Strain1541$PercentInhib)
estimates_1542 <- get_estimates(Strain1542$Concentration,Strain1542$PercentInhib)
estimates_1544 <- get_estimates(Strain1544$Concentration,Strain1544$PercentInhib)
estimates_1546 <- get_estimates(Strain1546$Concentration,Strain1546$PercentInhib)
estimates_1642 <- get_estimates(Strain1642$Concentration,Strain1642$PercentInhib)

```

#Graph the FlucR Strains and Clioquinol#
```{r}
GRAPH_Clioquinol_R <- ggplot(Strain1541_Summary)+
    geom_point(aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1541"))+
    geom_line(data=estimates_1541, aes(x=estimates_1541$x, y=estimates_1541$y, color="Strain1541"))+
    geom_point(data=Strain1542_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1542"))+
    geom_line(data=estimates_1542, aes(x=estimates_1542$x, y=estimates_1542$y, color="Strain1542"))+
    geom_point(data=Strain1544_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1544"))+
    geom_line(data=estimates_1544, aes(x=estimates_1544$x, y=estimates_1544$y,color="Strain1544"))+
    geom_point(data=Strain1546_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1546"))+
    geom_line(data=estimates_1546, aes(x=estimates_1546$x, y=estimates_1546$y,color="Strain1546"))+
    geom_point(data=Strain1642_Summary, aes(x=log10(Concentration), y=mean_PercentInhib, color="Strain1642"))+
    geom_line(data=estimates_1642, aes(x=estimates_1642$x, y=estimates_1642$y,color="Strain1642"))+
    scale_x_continuous(breaks=c(-3,-2,-1,0,1,2,3))+
    ylim(-0.35,1.25)+
    xlim(-3,2)+
    xlab("Clioquinol (uM)") + ylab("Percent Inhibition")+
    scale_color_manual(values=c(Green,Navy,Orange,Pink,Cyan,Purple))+
    ggtitle("Susceptible Strains")+
    theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
GRAPH_Clioquinol_R
ggsave(filename="GRAPH-Average_Clioquinol_R.pdf", plot=GRAPH_Clioquinol_R, useDingbats=FALSE, width=11, height=8.5, units="in")

Table <- matrix(data = NA, nrow =  5, ncol = 4, dimnames=list(c(1:5),c("Strain","EC50","EC50-min","EC50-max")))
Table[c(1:5),c(1)] <- FlucR
Table[c(1),c(2:4)] <- as.matrix(estimates_1541[c(1),c(3:5)])
Table[c(2),c(2:4)] <- as.matrix(estimates_1542[c(1),c(3:5)])
Table[c(3),c(2:4)] <- as.matrix(estimates_1544[c(1),c(3:5)])
Table[c(4),c(2:4)] <- as.matrix(estimates_1546[c(1),c(3:5)])
Table[c(5),c(2:4)] <- as.matrix(estimates_1642[c(1),c(3:5)])

Table_Clioquinol_R <- Table
write.table(Table_Clioquinol_R,"Table_Clioquinol_R.txt", sep="\t", quote=F, row.names = F)
```

Arrange All Clioquinol Graphs
```{r}
Clioquinol <- grid.arrange(GRAPH_Clioquinol_S,GRAPH_Clioquinol_M,GRAPH_Clioquinol_R, nrow=1, ncol=3)
ggsave("GRAPH-Clioquinol_Fit.pdf", plot=Clioquinol, useDingbats=FALSE, width=11, height=2.5, units="in")
```

Combine all Tables
```{r}
Clioquinol_Table <- rbind(Table_Clioquinol_S, Table_Clioquinol_M, Table_Clioquinol_R)
write.table(Clioquinol_Table,"Table_Clioquinol.txt", sep="\t", quote=F, row.names = F)

```

#Make Table of Data for Heatmap#
```{r}
Strain124_HR <- Strain124_Summary[,c(1:4)]
Strain124_Wide <- as.data.frame(t(Strain124_HR[,c(3:4)]))
colnames(Strain124_Wide) <- Strain124_Wide[c(1),]
row.names(Strain124_Wide) <- c("Concentration", "Strain124")
Strain124_Wide$Drug <- Strain124_HR[c(1:2),c(2)]
Strain124_Wide$Strain <- Strain124_HR[c(1:2),c(1)]

Strain1537_HR <- Strain1537_Summary[,c(1:4)]
Strain1537_Wide <- as.data.frame(t(Strain1537_HR[,c(3:4)]))
colnames(Strain1537_Wide) <- Strain1537_Wide[c(1),]
row.names(Strain1537_Wide) <- c("Concentration", "Strain1537")
Strain1537_Wide$Drug <- Strain1537_HR[c(1:2),c(2)]
Strain1537_Wide$Strain <- Strain1537_HR[c(1:2),c(1)]

Strain1538_HR <- Strain1538_Summary[,c(1:4)]
Strain1538_Wide <- as.data.frame(t(Strain1538_HR[,c(3:4)]))
colnames(Strain1538_Wide) <- Strain1538_Wide[c(1),]
row.names(Strain1538_Wide) <- c("Concentration", "Strain1538")
Strain1538_Wide$Drug <- Strain1538_HR[c(1:2),c(2)]
Strain1538_Wide$Strain <- Strain1538_HR[c(1:2),c(1)]

Strain1539_HR <- Strain1539_Summary[,c(1:4)]
Strain1539_Wide <- as.data.frame(t(Strain1539_HR[,c(3:4)]))
colnames(Strain1539_Wide) <- Strain1539_Wide[c(1),]
row.names(Strain1539_Wide) <- c("Concentration", "Strain1539")
Strain1539_Wide$Drug <- Strain1539_HR[c(1:2),c(2)]
Strain1539_Wide$Strain <- Strain1539_HR[c(1:2),c(1)]

Strain1540_HR <- Strain1540_Summary[,c(1:4)]
Strain1540_Wide <- as.data.frame(t(Strain1540_HR[,c(3:4)]))
colnames(Strain1540_Wide) <- Strain1540_Wide[c(1),]
row.names(Strain1540_Wide) <- c("Concentration", "Strain1540")
Strain1540_Wide$Drug <- Strain1540_HR[c(1:2),c(2)]
Strain1540_Wide$Strain <- Strain1540_HR[c(1:2),c(1)]

Strain1541_HR <- Strain1541_Summary[,c(1:4)]
Strain1541_Wide <- as.data.frame(t(Strain1541_HR[,c(3:4)]))
colnames(Strain1541_Wide) <- Strain1541_Wide[c(1),]
row.names(Strain1541_Wide) <- c("Concentration", "Strain1541")
Strain1541_Wide$Drug <- Strain1541_HR[c(1:2),c(2)]
Strain1541_Wide$Strain <- Strain1541_HR[c(1:2),c(1)]

Strain1542_HR <- Strain1542_Summary[,c(1:4)]
Strain1542_Wide <- as.data.frame(t(Strain1542_HR[,c(3:4)]))
colnames(Strain1542_Wide) <- Strain1542_Wide[c(1),]
row.names(Strain1542_Wide) <- c("Concentration", "Strain1542")
Strain1542_Wide$Drug <- Strain1542_HR[c(1:2),c(2)]
Strain1542_Wide$Strain <- Strain1542_HR[c(1:2),c(1)]

Strain1543_HR <- Strain1543_Summary[,c(1:4)]
Strain1543_Wide <- as.data.frame(t(Strain1543_HR[,c(3:4)]))
colnames(Strain1543_Wide) <- Strain1543_Wide[c(1),]
row.names(Strain1543_Wide) <- c("Concentration", "Strain1543")
Strain1543_Wide$Drug <- Strain1543_HR[c(1:2),c(2)]
Strain1543_Wide$Strain <- Strain1543_HR[c(1:2),c(1)]

Strain1544_HR <- Strain1544_Summary[,c(1:4)]
Strain1544_Wide <- as.data.frame(t(Strain1544_HR[,c(3:4)]))
colnames(Strain1544_Wide) <- Strain1544_Wide[c(1),]
row.names(Strain1544_Wide) <- c("Concentration", "Strain1544")
Strain1544_Wide$Drug <- Strain1544_HR[c(1:2),c(2)]
Strain1544_Wide$Strain <- Strain1544_HR[c(1:2),c(1)]

Strain1545_HR <- Strain1545_Summary[,c(1:4)]
Strain1545_Wide <- as.data.frame(t(Strain1545_HR[,c(3:4)]))
colnames(Strain1545_Wide) <- Strain1545_Wide[c(1),]
row.names(Strain1545_Wide) <- c("Concentration", "Strain1545")
Strain1545_Wide$Drug <- Strain1545_HR[c(1:2),c(2)]
Strain1545_Wide$Strain <- Strain1545_HR[c(1:2),c(1)]

Strain1546_HR <- Strain1546_Summary[,c(1:4)]
Strain1546_Wide <- as.data.frame(t(Strain1546_HR[,c(3:4)]))
colnames(Strain1546_Wide) <- Strain1546_Wide[c(1),]
row.names(Strain1546_Wide) <- c("Concentration", "Strain1546")
Strain1546_Wide$Drug <- Strain1546_HR[c(1:2),c(2)]
Strain1546_Wide$Strain <- Strain1546_HR[c(1:2),c(1)]

Strain1641_HR <- Strain1641_Summary[,c(1:4)]
Strain1641_Wide <- as.data.frame(t(Strain1641_HR[,c(3:4)]))
colnames(Strain1641_Wide) <- Strain1641_Wide[c(1),]
row.names(Strain1641_Wide) <- c("Concentration", "Strain1641")
Strain1641_Wide$Drug <- Strain1641_HR[c(1:2),c(2)]
Strain1641_Wide$Strain <- Strain1641_HR[c(1:2),c(1)]

Strain1642_HR <- Strain1642_Summary[,c(1:4)]
Strain1642_Wide <- as.data.frame(t(Strain1642_HR[,c(3:4)]))
colnames(Strain1642_Wide) <- Strain1642_Wide[c(1),]
row.names(Strain1642_Wide) <- c("Concentration", "Strain1642")
Strain1642_Wide$Drug <- Strain1642_HR[c(1:2),c(2)]
Strain1642_Wide$Strain <- Strain1642_HR[c(1:2),c(1)]

Strain1643_HR <- Strain1643_Summary[,c(1:4)]
Strain1643_Wide <- as.data.frame(t(Strain1643_HR[,c(3:4)]))
colnames(Strain1643_Wide) <- Strain1643_Wide[c(1),]
row.names(Strain1643_Wide) <- c("Concentration", "Strain1643")
Strain1643_Wide$Drug <- Strain1643_HR[c(1:2),c(2)]
Strain1643_Wide$Strain <- Strain1643_HR[c(1:2),c(1)]

StrainB3_HR <- StrainB3_Summary[,c(1:4)]
StrainB3_Wide <- as.data.frame(t(StrainB3_HR[,c(3:4)]))
colnames(StrainB3_Wide) <- StrainB3_Wide[c(1),]
row.names(StrainB3_Wide) <- c("Concentration", "StrainB3")
StrainB3_Wide$Drug <- StrainB3_HR[c(1:2),c(2)]
StrainB3_Wide$Strain <- StrainB3_HR[c(1:2),c(1)]

StrainB8_HR <- StrainB8_Summary[,c(1:4)]
StrainB8_Wide <- as.data.frame(t(StrainB8_HR[,c(3:4)]))
colnames(StrainB8_Wide) <- StrainB8_Wide[c(1),]
row.names(StrainB8_Wide) <- c("Concentration", "StrainB8")
StrainB8_Wide$Drug <- StrainB8_HR[c(1:2),c(2)]
StrainB8_Wide$Strain <- StrainB8_HR[c(1:2),c(1)]

Strains_Wide <- merge(merge(merge(merge(merge(merge(merge(merge(merge(merge(merge(merge(merge(merge(merge(Strain1537_Wide[c(2),], Strain1538_Wide[c(2),],all=TRUE),Strain1543_Wide[c(2),],all=TRUE),Strain124_Wide[c(2),], all=TRUE),StrainB3_Wide[c(2),], all=TRUE),StrainB8_Wide[c(2),], all=TRUE),Strain1539_Wide[c(2),],all=TRUE), Strain1540_Wide[c(2),], all=TRUE), Strain1545_Wide[c(2),], all=TRUE), Strain1641_Wide[c(2),], all=TRUE), Strain1643_Wide[c(2),], all=TRUE), Strain1541_Wide[c(2),], all=TRUE), Strain1542_Wide[c(2),], all=TRUE), Strain1544_Wide[c(2),], all=TRUE), Strain1546_Wide[c(2),],all=TRUE),Strain1642_Wide[c(2),], all=TRUE)

write.table(Strains_Wide, "Clioquinol_Strains_Wide.txt", sep="\t", row.names=F, quote=F)
```

